---
title: "Targeting A Housing Subsidy"
author: "Minwook Kang"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: cerulean
    highlight: monochrome
    css: custom.css
---

<style>
div.blue pre.r { background-color:#eff3ff; }
</style>


## Ⅰ. Setup 

This is section for libraries, functions and overall styling settings.

<div class = "blue">
```{r message=FALSE, warning=FALSE}

# Rmarkdown global setting
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(cache = TRUE)
knitr::opts_chunk$set(fig.align = 'center')

#----------------------------------------------------------------------------------------------------------  

# Import libraries
library(tidyverse)
library(tidycensus)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot)# plot correlation plot
library(corrplot)
library(corrr)      # another way to plot correlation plot
library(kableExtra)
library(jtools)     # for regression model plots
library(ggstance) # to support jtools plots
library(ggpubr)    # plotting R^2 value on ggplot point scatter
library(broom.mixed) # needed for effects plots
library(knitr)
library(rmarkdown)
library(RSocrata)
library(viridis)
library(ggplot2)
library(stargazer)
library(XML)
library(data.table)
library(ggpmisc)
library(patchwork)
library(spatstat)
library(raster)
library(classInt)   # for KDE and ML risk class intervals
library(tableHTML)

#----------------------------------------------------------------------------------------------------------  

# Temp
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")
root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"

# Etc
options(scipen=999)
options(tigris_class = "sf")

#----------------------------------------------------------------------------------------------------------  

# functions

st_c    <- st_coordinates
st_coid <- st_centroid

mapThememin <- function(base_size = 10, title_size = 12, small_size = 8) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = title_size, colour = "black", hjust = 0.5),
    plot.subtitle=element_text(size = base_size, colour = "black", hjust = 0.5, face="italic"),
    plot.caption=element_text(size = small_size, colour = "black", hjust = 0.5),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    strip.text.x = element_text(size = small_size, face="italic"),
    strip.text.y = element_text(size = small_size, face="italic"),
    strip.background = element_rect(colour="transparent", fill="transparent"),
    legend.title = element_text(size = small_size),
    legend.text = element_text(size = small_size),
    legend.key.size = unit(0.4, "cm"))
}

mapThememin2 <- function(base_size = 8, title_size = 10, small_size = 6) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = title_size, colour = "black", hjust = 0.5),
    plot.subtitle=element_text(size = base_size, colour = "black", hjust = 0.5, face="italic"),
    plot.caption=element_text(size = small_size, colour = "black", hjust = 0.5),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    strip.text.x = element_text(size = base_size),
    strip.text.y = element_text(size = base_size),
    strip.background = element_rect(colour="transparent", fill="transparent"),
    legend.title = element_text(size = small_size),
    legend.text = element_text(size = small_size),
    legend.key.size = unit(0.25, "cm"))
}


corTheme <- function(base_size = 10, title_size = 12, small_size = 8){
  theme(axis.text =  element_blank(), 
        axis.ticks = element_blank(), 
        text = element_text(size = 10),
        panel.background = element_rect(fill = greyPalette5[1]),
        axis.title.x = element_text(size = small_size),
        axis.title.y = element_text(size = small_size),
        plot.subtitle = element_text(hjust = 0.5, size = base_size),
        plot.title = element_text(hjust = 0.5, size = title_size),
        plot.caption=element_text(size = small_size, colour = "black", hjust = 0.5),
        strip.background = element_rect(colour="transparent", fill="transparent"))
}


corTheme2 <- function(base_size = 10, title_size = 12, small_size = 8){
  theme(axis.text =  element_text(size = small_size),
        text = element_text(size = 10),
        panel.background = element_rect(fill = greyPalette5[1]),
        axis.title.x = element_text(size = small_size),
        axis.title.y = element_text(size = small_size),
        plot.subtitle = element_text(hjust = 0.5, size = base_size,  face="italic"),
        plot.title = element_text(hjust = 0.5, size = title_size),
        plot.caption=element_text(size = small_size, colour = "black", hjust = 0.5),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(size = small_size, face="italic"),
        strip.text.y = element_text(size = small_size, face="italic"))
}

corTheme3 <- function(base_size = 9, title_size = 11, small_size = 7){
  theme(axis.text =  element_text(size = small_size),
        text = element_text(size = 10),
        panel.background = element_rect(fill = greyPalette5[1]),
        axis.title.x = element_text(size = small_size),
        axis.title.y = element_text(size = small_size),
        plot.subtitle = element_text(hjust = 0.5, size = base_size,  face="italic"),
        plot.title = element_text(hjust = 0.5, size = title_size),
        plot.caption=element_text(size = small_size, colour = "black", hjust = 0.5))
}

corTheme4 <- function(base_size = 9, title_size = 11, small_size = 7){
  theme(axis.text =  element_text(size = small_size),
        text = element_text(size = 10),
        panel.background = element_rect(fill = greyPalette5[1]),
        axis.title.x = element_text(size = small_size),
        axis.title.y.right = element_text(size = small_size),
        plot.subtitle = element_text(hjust = 0.5, size = base_size,  face="italic"),
        plot.title = element_text(hjust = 0.5, size = title_size),
        plot.caption=element_text(size = small_size, colour = "black", hjust = 0.5))
}


q5 <- function(variable) {as.factor(ntile(variable, 5))}

q <- function(variable) {as.factor(ntile(variable, 5))}

qBr <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(quantile(round(df[[variable]],0),
                          c(.01,.2,.4,.6,.8), na.rm=T))
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]],
                                  c(.01,.2,.4,.6,.8), na.rm=T),
                         digits = 3))
  }
}

qBr2 <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(quantile(round(df[[variable]]*100,0)/100,
                          c(.01,.2,.4,.6,.8), na.rm=T))
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]],
                                  c(.01,.2,.4,.6,.8), na.rm=T),
                         digits = 3))
  }
}

qBr3 <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(round(quantile(round(df[[variable]]*1000000,0),
                          c(.01,.2,.4,.6,.8), na.rm=T)),0)
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]],
                                  c(.01,.2,.4,.6,.8), na.rm=T),
                         digits = 3))
  }
}

substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}


nn_function <- function(measureFrom,measureTo,k) {
  measureFrom_Matrix <- as.matrix(measureFrom)
  measureTo_Matrix <- as.matrix(measureTo)
  nn <- get.knnx(measureTo, measureFrom, k)$nn.dist
  output <- as.data.frame(nn) %>%
    rownames_to_column(var = "thisPoint") %>%
    gather(points, point_distance, V1:ncol(.)) %>%
    arrange(as.numeric(thisPoint)) %>%
    group_by(thisPoint) %>%
    summarize(pointDistance = mean(point_distance)) %>%
    arrange(as.numeric(thisPoint)) %>% 
    dplyr::select(-thisPoint) %>%
    pull()
  return(output)  
}


myCrossValidate <- function(dataset, id, dependentVariable, indVariables) {
  
  allPredictions <- data.frame()
  cvID_list <- unique(dataset[[id]])
  
  for (i in cvID_list) {
    
    thisFold <- i
    cat("This hold out fold is", thisFold, "\n")
    
    fold.train <- filter(dataset, dataset[[id]] != thisFold) %>% as.data.frame() %>% 
      dplyr::select(id, geometry, indVariables, dependentVariable)
    fold.test  <- filter(dataset, dataset[[id]] == thisFold) %>% as.data.frame() %>% 
      dplyr::select(id, geometry, indVariables, dependentVariable)
    
    regression <-
      glm(countMVTheft ~ ., family = "poisson", 
          data = fold.train %>% 
            dplyr::select(-geometry, -id))
    
    thisPrediction <- 
      mutate(fold.test, Prediction = predict(regression, fold.test, type = "response"))
    
    allPredictions <-
      rbind(allPredictions, thisPrediction)
    
  }
  return(st_sf(allPredictions))
}

#----------------------------------------------------------------------------------------------------------  

# Colors ("https://coolors.co/gradient-palette/a8f368-f9035e?number=7")
bluePalette5 <- c("#eff3ff","#bdd7e7","#6baed6","#3182bd","#08519c")
blue2Palette5 <- c("#08519c","#3182bd","#6baed6","#bdd7e7","#eff3ff")
H_bluePalette5 <- c("#eff3ff","#bdd7e7","#6baed6","#3182bd","#252525")
orangePalette5 <- c("#FFF2E8","#FFD6B6","#FEB984","#FE9D51","#FD801F")
orange2Palette5 <- c("#FFDFD0","#FFB89F","#FF926E","#FF6B3D","#FF440C")
greyPalette5 <- c("#f7f7f7","#cccccc","#969696","#636363","#252525")
greenPalette5 <- c("#edf8e9","#bae4b3","#74c476","#31a354","#006d2c")
purplePalette5 <- c("#f2f0f7","#cbc9e2","#9e9ac8","#756bb1","#54278f")

#----------------------------------------------------------------------------------------------------------  

# LoadAPI(Min's key)
census_api_key("4bbe4bead4e5817f6a6b79e62c5bea69e77f1887", overwrite = TRUE)


```
</div>

## Ⅱ. Data

<div class = "blue">
```{r message=FALSE, warning=FALSE}

# Tracts geometry, Census Information

housingSubsidy <- read.csv("https://github.com/urbanSpatial/Public-Policy-Analytics-Landing/raw/master/DATA/Chapter6/housingSubsidy.csv")

summary(housingSubsidy)

```
</div>

## Ⅲ. Process

### 1. Motivation for analysis
(One paragraph on the motivation for the analysis)



### 2. Exploratory analysis
(Develop and interpret data visualizations that describe feature importance/correlation)

<div class = "blue">
```{r message=FALSE, warning=FALSE, out.width = '100%'}

housingSubsidy %>%
  gather(Variable, value, -y) %>%
    ggplot(aes(y, value, fill=y)) + 
      geom_bar(position = "dodge", stat = "summary", fun = "mean") + 
      facet_wrap(~Variable, scales = "free") +
      scale_fill_manual(values = palette2) +
      labs(x="Click", y="Value", 
           title = "Feature associations with the likelihood of click",
           subtitle = "(continous outcomes)") +
      theme(legend.position = "none")

```
</div>


### 3. Training/Testing sets
(Split your data into a 65/35 training/test set)

In this section, training and test sets are created. createDataPartition is used to split the data. A 65% sample is used here to reduce processing time.

<div class = "blue">
```{r message=FALSE, warning=FALSE, out.width = '100%'}


```
</div>

### 4. Feature Engineering
(The Sensitivity (True Positive Rate) for a model with all the features is very low. Engineer new features that significantly increase the Sensitivity)
(Interpret your new features in one paragraph)
(Show a regression summary for both the kitchen sink and your engineered regression)
(Cross validate both models; compare and interpret two facetted plots of ROC, Sensitivity and Specificity)

<div class = "blue">
```{r message=FALSE, warning=FALSE, out.width = '100%' }


```
</div>

### 5. ROC curve

<div class = "blue">
```{r message=FALSE, warning=FALSE, out.width = '100%'}


```
</div>

### 6. Cost/Benefit analysis
(Develop a cost benefit analysis)
(Write out the cost/benefit equation for each confusion metric)
(Create the ‘Cost/Benefit Table’ as seen above)
(Plot the confusion metric outcomes for each Threshold)
(Create two small multiple plots that show threshold as a function of total_revenue and total_count_of_credits. Interpret this)
(Create a table of the total_revenue and total_count_of_credits allocated for 2 categories. 50%_threshold and and your optimal_threshold)

<div class = "blue">
```{r message=FALSE, eval=TRUE, warning=FALSE, include=FALSE}


```


## Ⅳ. Conclustion

While we were able to confirm that models using Hotspot have a high degree of generalization, we have not shown good results in capturing crimes in high-risk areas. Even if you've shown good results, you can't be sure that the real model is not biased. Therefore, it would be desirable to use a model that predicts this risk for events such as fires that do not bias real data collection.

























































